Title

### 2023-06-22 main.tex
Your heart's been aching but you're too shy to say it

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open quantum systems, 
which can be described by the theory of quantum
channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{red} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
\cpnote{Se siente forzada. nos toca encontrar mas ejemplos e introducirla de
manera mas natural. Quizá mas adelante}
\tbnote{Va, es cierto.
Puedo incluir más trabajos y hablarlo más en general para que no se sienta forzado:}
{\color{purple}
Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
}

Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Davalos,Zbigniew,geometry}, 
\cpnote{Aca citar nuestros trabajos con Davalos. } \tbnote{Ya agregué la cita}
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
\cpnote{Creo que la transición de general a particular va demasiado rapido. Quizá hacerle 
ver a Tomas y luego reescribirlo yo}
\tbnote{Va, sí lo veo, gracias!}

\cpnote{De nuevo una transicion muy abrupta. Para que ver los circuitos? Priero 
hablar de los circuitos, quizá una frase, luego hablar de los parametrizadso, 
Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
\tbnote{Lo de Barreiro es una de las citas que agregué nuevas arriba}
\tbnote{Para lo de lo abrupto, quizá una frase como:} 
{\color{purple} To represent the algorithms
done in quantum computers, either
to simulate a physical system or for some other purpose,
one often uses a quantum circuit~\cite{chuangbook}.}
In this work, we shall also work with parametrized quantum circuits, that is,  
quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
These circuits play an important 
part in applications such as quantum machine learning~\cite{Benedetti}
and describing general quantum transformations dependent on parameters. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

% In this article, our first objective is to present a 
% quantum algorithm capable of simulating Pauli channels on quantum computers, 
% and we demonstrate its implementation using IBM's quantum computers. 
% This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
% and works by utilizing $2N$ ancilla qubits.
% 
% Expanding beyond discrete Pauli channels,
% we introduce the concept of Pauli dynamical maps, 
% defined as a continuous parametrization of
% $N$-qubit Pauli channels. 
% We adapt the algorithm developed for Pauli channels 
% to accommodate these dynamical maps by employing a 
% parametrized quantum circuit. 
% Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
% which outlines the types of transformations that 
% can be done using a parametrized circuit with the condition that only one
%  single-qubit operation in the circuit may depend on the parameter.
% We explicitly find the mathematical conditions for these types of
% transformations and conclude about which 
% Pauli dynamical maps can be done with them. 
% \cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
% y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
% integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
% \tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}
%

{\color{purple}  
In this article,
after providing the definition of quantum
channels and $N$-qubit Pauli channels
in section \ref{sec: Pauli Channels},
 our first objective is to present a 
quantum algorithm capable of simulating Pauli channels on quantum computers.
We do this in section \ref{sec: Circuit for a Pauli Channel},
where we also demonstrate its implementation using IBM's quantum computers for 
the particular case of single-qubit Pauli channels.

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
Therefore, in section \ref{sec: 1PR Circuits}
we shift our focus to study parametrized
quantum channels, 
aiming to
adapt the algorithm developed for channels 
to dynamical maps. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which  sets the mathematical conditions for the transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map},
we conclude about the 
Pauli dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
}

@@

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a high $f$, while those 
close to unitary channels have much lower $f$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes. Moreover, the algorithm of \fref{fig:
circuit-pauli-1} is not optimal for unitary channels (that is, the channels
corresponding to the vertices of the tetrahedron).  These straightforward
channels could be accomplished more efficiently by simply applying the
corresponding Pauli operation directly. Nevertheless, due to its general design
to accommodate any Pauli channel, the algorithm employs numerous quantum gates
even in such scenarios.
\cpnote{Iterar este parrafo cuando estemos cerca del final. Ta un tilin chafa.}

@@

For the particular case of one qubit, we can show some examples of Pauli
dynamical maps implementable with a 1PR circuit, which are plotted in
\fref{fig:curves1}. 
{\color{purple} The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
However, we also include a more uncommon map, which we call the parabolic dynamical map,
defined in \eref{eq:parab} and shown in \fref{fig:curves1}.
This map traces a parabola inside the tetrahedron connecting two of its vertices
and it describes a frontier in the tetrahedron between Pauli channels
that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.
}

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
Then, taking the $\beta_j$ to be real,
this curve of states can be \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.} 
\tbnote{Sí es correcto, va}
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. } \tbnote{Va, listo, lo puse en morado}
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
\label{eq:parab}
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits can be:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
\cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
\tbnote{No, no lo hago con CUE ni nada así por lo de que el
primer renglon debe de tner una forma particular y no sabría cómo agregar eso tras
elegir una matriz de CUE.}
\tbnote{Lo que hago es empezar con ese renglon y busco un segundo renglón que sea ortogonal al primero y normalizado.
Para ello, tomo tres vectores $w_1, w_2, w_3$
normalizados y ortogonales al primer renglon.
Entonces, el segundo renglon será en general
de la forma $r_1 w_1 + r_2 w_2 + r_3 w_3$
con $r_i$ complejos y que $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ (para que el 
segundo renglon esté normalizado).
Entonces, busco esos $r_1, r_2, r_3$ al azar  
(básicamente las partes reales e imaginarias
de las $r_i$ deben de estar en una 6-esfera,
por lo que escojo un punto al azar en dicha esfera).}

and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

However, since a Pauli dynamical map should begin at the
identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
$\theta$ an arbitrary real number. 
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
acomode bien a lo que ambos nos parezca.}
\tbnote{Jaja sí, va}\\

{\color{purple}
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ an arbitrary real number.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of \eref{eq:conditions-vecs}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

The choice of such a matrix $V$ can be done at random as follows:
After setting the first row,
construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to it
using the Gram-Schmidt process.
Then select random complex numbers $r_1, r_2, r_3$ such
that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and
define the second row of $V$ to be
$r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.
}

@@

\section{Conclusion} % {{{
\tbnote{Primera versión para ir teniendo algo escrito }\\

In this work, we focused on the analysis of Pauli channels in $N$-qubit systems and
developed an algorithm to implement them on a quantum computer.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much straightforward manner.
{\color{purple}
Consequently, this work presents another example of the
simulation of open quantum systems, and their
implementation in a quantum computer. }

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.
{\color{purple} Therefore, it can be useful for simplifying any algorithm
that requires a parametrized quantum circuit,
such as those for quantum machine learning.}

\cpnote{Leiste como escribir una conclusion? Aca falta algo importante. Si ya lo leiste, 
dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
muy buena primera iteracion para las conclusiones!! }
\tbnote{Ah, supongo que lo de volver a expandir y hablar en general para terminar de hacer la forma de ``hourglass''
en el artículo. Agregué algo en morado para eso.}

\tbnote{Mejor quitar todo lo anterior y dejar esto:}

@@

\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
acknowledged.

>>>>

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}. 
% Several 
% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts
towards the simulation of the evolution of open quantum
systems~\cite{cleve,Zanetti,Xin,Wei}\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}.
Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and withing them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
quantum circuits, that is,  quantum circuits in which some of the operations
depend on variable parameters~\cite{cerezo}.  These circuits play an important
part in applications such as quantum machine learning~\cite{Benedetti} and
describing general quantum transformations dependent on parameters. Substantial
research has been devoted to enhancing the efficiency of these
circuits~\cite{Watanabe,Rasmussen}.

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the condition that only a
controlled \cpnote{el caso general es controlado, correcto?} single-qubit
operation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{fig:fids} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$.  This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{fig: circuit-pauli-1} is not optimal for
unitary channels (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly.
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios.

@@

For the particular case of one qubit, we can show some examples of Pauli
dynamical maps implementable with a 1PR circuit, which are plotted in
\fref{fig:curves1}. 
The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
However, we also include the parabolic dynamical map,
defined in \eref{eq:parab} and shown in \fref{fig:curves1}.
This map traces a parabola inside the tetrahedron connecting two of its vertices
and it describes a frontier in the tetrahedron between Pauli channels
that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that ${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 =
{|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.  Then, taking the $\beta_j$ to be
real, the curve of states can be 
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
\label{eq:parab}
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits can be:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] 
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ a uniform random phase.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
\eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
unitaria. Aclarame ese punto y le sigo al resto del parrafo}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.
Next, construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
the first row using the Gram-Schmidt process.  Then select random complex
numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and define
the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.
\end{itemize}

@@

\section{Conclusion} % {{{

\cpnote{Reitera. Dale a lo qeu discutimos el espacio. a lo de la decoherencia nota
que no lo tomamos como un resultado importante. Aca le das mucho mas espacio 
del que croe que merece. Inspirate en la intro. }

@@

\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
